\documentclass[prodmode]{acmlarge}

% Metadata Information
\acmVolume{0}
\acmNumber{0}
\acmArticle{0}
\articleSeq{0}
\acmYear{2013}
\acmMonth{5}

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\SetAlFnt{\algofont}
\SetAlCapFnt{\algofont}
\SetAlCapNameFnt{\algofont}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}
\renewcommand{\algorithmcfname}{ALGORITHM}


% Page heads
\markboth{J.~Overbey}{Immutable Source-Mapped Abstract Syntax Tree}

% Title portion
\title{Immutable Source-Mapped Abstract Syntax Tree: \\
A Design Pattern for Refactoring Engine APIs}
\author{JEFFREY L.\ OVERBEY \affil{Auburn University}}

\begin{abstract}
TODO
\end{abstract}

\category{X.0.0}{TODO}{TODO}[TODO]

\terms{TODO}
\keywords{TODO}

\acmformat{Overbey, J. 2013. Immutable Source-Mapped Abstract Syntax Tree.}

\copyr{PLoP'13, October 23--26, Monticello, Illinois, USA. Copyright 2013 is
held by the author(s). ACM 978-1-4503-0107-7}

\begin{document}

\begin{bottomstuff}
This material is based upon work supported by the National Science Foundation
under Grant No.~CCF-1217271.

Permission to make digital or hard copies of all or part of this work for
personal or classroom use is granted without fee provided that copies are not
made or distributed for profit or commercial advantage and that copies bear
this notice and the full citation on the first page. To copy otherwise, to
republish, to post on servers or to redistribute to lists, requires prior
specific permission. A preliminary version of this paper was presented in a
writers' workshop at the 20th Conference on Pattern Languages of Programs
(PLoP).
\end{bottomstuff}


\maketitle

%\section{Abstract}
%\section{Example}
%\section{Context}
%\section{Problem}
%\section{Solution}
%\section{Structure}
%\section{Dynamics}
%\section{Implementation}
%\section{Example Resolved}
%\section{Variants}
%\section{Known Uses}
%\section{Consequences}
%\section{See Also}
%\section{Credits}

\section{Context}

\cite{TODO}

\section{Problem}

\section{Forces}

\section{Solution}
=> Rewrite text directly
=> Rewrite to new AST

\section{Example}

\section{Known Uses}
JDT
Red-Green Trees - MS
CDT
Clang
NetBeans???
gorf???

\section{Related Patterns and Guidelines}

\bibliographystyle{acmlarge}
\bibliography{paper}

% History dates
%\received{February 2009}{July 2009}{October 2009}

\end{document}

